---
title: "Bristol Bay Sockeye Salmon Runs"
author: "Levi Rucka"
date: '2022-12-06'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bristol Bay is a complex fishing region of southwest Alaska
- Fishing districts of Alagnak, Egegik, Igushik,
Kvichak, Naknek, Nushagak, Togiak,
Ugashik, and Wood rivers.

![Alttext](https://www.researchgate.net/profile/Ray-Hilborn-2/publication/10763829/figure/fig5/AS:667121893797890@1536065662190/Map-of-Bristol-Bay-Alaska-showing-the-major-lake-systems-producing-sockeye-salmon-and_W640.jpg)

## Slide with Bullets
- Boats during the Fishing season (June 10 – July 25) race to catch fish
- Boats have gotten bigger recently compared to previous fishing seasons
```{r pressure}
plot(pressure)
```

